\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-02-03 tex/paper.tex
Added some future work

%}}}
\begin{abstract}
    \fix Abstract

@@

%}}}
\section{Introduction}
Developing larger projects containing static content usually involves using a Content Distribution
Network to be able to scale to a large user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then distributed over the globe when the public requests it. For secret content this can be a
problem and an inconvenience, and that is what this thesis is about. This work examines ways of
enforcing virtual access control on content and groups of content, in the form of folders and
snapshots. A system was developed to make the underlying theory work in practice.

@@

\fix Clarify problem definition and research questions
\section{Background}
\subsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming
experiences, which means that they are mostly not focussed on the actual gameplay which other EA 
studios like DICE is.

@@

\newpage

\label{sec:model}
\section{Model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the integrity of the data is always kept in the Perius system.

@@

As this work only presents an informal model of how the system is designed it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should how ever give a 
strong idea of the soundness of the designed system.

@@

\label{sec:conseq}
\subsection{Consequences of modification}

@@

\subsection{Interaction of Multiple Accesses}
\fix Rename consequence?

As a result of consequence~\ref{eq:contentupdate} and~\ref{eq:containerupdate} there can be race
conditions where the last write wins. This could be solved by locks or transactions, but as updates
are not based on each other, the trade-off for this inconsistency to scalability and speed is
intentional. However as can also be seen in consequence~\ref{eq:fileupdate}, if a file is
removed from a content that file is not removed from the set of files, even though its modification
process is not the last one to write to the content. This is necessary as a file can be referenced
from several content and the removal process can not atomically ensure that the file is not referred
to by another content. This results in a lot of files in the system which are not referenced from
anywhere. This can be solved by either making each file keep track of how many times it is referred
to and also make it possible to check this number and delete the file in an atomic fashion. An
easier approach would be to have a garbage collector which locks parts of the system momentarily
meanwhile it removes files which are not referenced.

There is also the chance to have content and containers that are not referenced from anywhere and
result in being garbage in the system. This could happen as a result of consequence~\ref{eq:delete}
in combination with any of the other consequences listed in Section~\ref{sec:conseq}. The basic idea
is that an entity is deleted meanwhile another is created or modified to have that entity as its
parent and thus creating a separate tree that can not be reached from the root node of the project.

\subsection{Findings}

@@

\subsubsubsection{Serving private content}
\fix Describe the different CDN mechanisms, like signed cookies and urls

There are three different ways, that this implementation make use of, to make sure that 
the CDNs serve content in a private manner. The first two is signed URLs and signed cookies, and 
the third is a mixture between one of the first two together with a range of IP
addresses.~\cite{AWSPRIVATE} 
These mechanisms are needed, as explained in Section~\ref{sec:current_system}, to ensure that
assets are not leaked if an attacker manages to find out the URL for the asset.

\par \textbf{Signed URLs} \\
test test

\par \textbf{Signed cookies} \\
test test

\par \textbf{IP range restriction} \\
test test

@@

\section{JPF}
\fix Not sure where to put this section

@@

\section{Discussion}

\section{Summary}
\subsection{Conclusions}

\subsection{Future work}
Full access control was not implemented according to the model described in ~\ref{sec:model}, it
was only implemented to check whether a user should have access to the system as a whole or not, the
implementation did not set or check any specific access rights to certain contents or containers.

>>>>

%}}}
\begin{abstract}
    \fix Abstract is written last

@@

%}}}
\section{Introduction}
Developing larger projects containing static content usually involves using a Content Distribution
Network to be able to scale to a large user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then distributed over the globe when the public requests it. For secret content this can be a
problem and an inconvenience, and that is what this thesis is about. This work examines ways of
enforcing virtual access control on content and groups of content, in the form of containers and
snapshots. A system was developed to make the underlying theory work in practice.

@@

\fix Clarify problem definition and research questions
\newpage
\section{Background}
\subsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming
experiences, which means that they are mostly not focussed on the actual gameplay which other EA 
studios like DICE is.

@@

\newpage
\label{sec:model}
\section{Model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the integrity of the data is always kept in the Perius system.

@@

As this work only presents an informal model of how the system is designed it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should how ever give a 
strong idea of the soundness of the design of the system.

@@

\subsection{Consequences of modification} \label{sec:conseq}

@@

\subsection{Interaction of Multiple Accesses} \label{sec:multiple_access}
\fix Rename consequence?
\\
As a result of consequence~\ref{eq:contentupdate} and~\ref{eq:containerupdate} there can be race
conditions where the last write wins. This could be solved by locks or transactions, but as updates
are not based on each other, the trade-off for this inconsistency to scalability and speed is
intentional. However as can also be seen in consequence~\ref{eq:fileupdate}, if a file is
removed from a content that file is not removed from the set of files, even though its modification
process is not the last one to write to the content. This is necessary as a file can be referenced
from several content and the removal process can not atomically ensure that the file is not referred
to by another content. This results in a lot of files in the system which are not referenced from
anywhere. This can be solved by either making each file keep track of how many times it is referred
to and also make it possible to check this number and delete the file in an atomic fashion. An
easier approach would be to have a garbage collector which locks parts of the system momentarily
meanwhile it removes files which are not referenced.
\\
There is also the chance to have content and containers that are not referenced from anywhere and
result in being garbage in the system. This could happen as a result of consequence~\ref{eq:delete}
in combination with any of the other consequences listed in Section~\ref{sec:conseq}. The basic idea
is that an entity is deleted meanwhile another is created or modified to have that entity as its
parent and thus creating a separate tree that can not be reached from the root node of the project.
These type of inconveniences should also be cleaned up by the garbage collector.

\subsection{Findings}
\fix Add more findings
\subsubsection{Garbage Collection}
For the system to reach the decided eventual consistency~\cite{KLINGSBO}, garbage collection will be
needed. As of the conclusion in Section~\ref{sec:multiple_access} from Section ~\ref{sec:conseq} 
there will be objects in the system that can not be reached and should therefore be cleaned up for 
them not to cause negative performance effects on the system.

@@

\subsubsubsection{Serving private content}
There are three different ways, that this implementation make use of, to make sure that 
the CDNs serve content in a private manner. The first two are signed URLs and signed cookies, and 
the third is a mixture between one of the first two together with a range of IP
addresses.~\cite{AWSPRIVATE} 
These mechanisms are needed, as explained in Section~\ref{sec:current_system}, to ensure that
assets are not leaked if an attacker manages to find out the URL for the asset.

\par \textbf{Signed URLs} \\
Signed URLs work by writing a policy statement that specifies the restrictions that should apply for
the asset the URL is referring to. There are two different types of these policies; canned and
custom. In the canned policy there is only an option to specify the date for when the URL is no 
longer valid. In the custom policy it is possible to also specify the date when the asset should be
made available, ranges of IP addresses (which is discussed more in a later paragraph) and inclusion
of the base64 version of the policy in the URL~\cite{AWSSIGNED}. For custom policies it is also 
possible to reuse the policy and have it refer to multiple assets.\\

\par \textbf{Signed cookies} \\
Signed cookies work very similarly to signed URLs, the same type of canned and custom policies can
be set, except for the policy to include the base64 version of the policy in the URL. Signed cookies
are to be used when the URL should remain static even though the policies change~\cite{AWSCOOKIES}.
\\

\par \textbf{IP range restriction} \\
The IP range restriction is presented as a third option in Perius, even though it in fact is just a
part of a Signed Cookie or URL policy. The IP range restriction makes it possible to restrict which
IP addresses that can access the asset, this option can be fitting when for example an office or
companies internet access is based on a set of public static IP addresses and thus restricts the
content from ever being accessed outside of that controlled network.

@@

\subsubsection{Security}
\fix Write what security implications that can be seen

\newpage
\section{JPF}
\fix Not sure where to put this section

@@

\newpage
\section{Discussion}
\subsection{Persistent Storage}
More research could have been done in the choosing of persistent storage, as mentioned in ``NoSQL:
Moving from MapReduce Batch Jobs to Event-Driven Data Collection''~\cite{KLINGSBO} many applications
that choose NoSQL databases as their persistent storage actually don't need it. This is most likely
true for Perius too, it would have been efficient enough generating the project trees from an
indexed SQL database with foreign keys. On the other hand it was quite nice having the BSON
documents for insertion as they were so similar the accepted JSON format from the REST service.
As Perius most common operations involve modifying the project tree, a graph database should have 
been researched too.

\newpage
\section{Summary}
\subsection{Conclusions}

\subsection{Future work}
\subsubsection{Access Control}
Full access control was not implemented according to the model described in ~\ref{sec:model}, it
was only implemented to check whether a user should have access to the system as a whole or not, the
implementation did not set or check any specific access rights to certain contents or containers.

\subsubsection{Front-end Refactor}
The application could be made substantially more efficient by rewriting the front-end to update
itself according to the REST response after a modification of the project tree, instead of 
re-fetching the full project tree every time a change is made.
